Concrete Semantics for Pushdown Analysis:\\The Essence of Summarization

### 2013-10-04 abstract.tex
More abstract changes.

Pushdown analysis is better than finite-state analysis in precision and
performance. Why then have we not seen total widespread adoption of these
techniques? For one, the known techniques are technically burdened and
difficult to understand or extend. Control structure of the programming language
gets pulled into the model of computation, which makes extensions to
non-pushdown control structures, such as \rackett{call/cc} or \rackett{shift} and
\rackett{reset}, non-trivial.

We show a derivational approach to abstract interpretation that yields
transparently sound static analyses that can precisely match calls and
returns when applied to well-known abstract machines. We show that
adding memoization and segmenting the continuation into bounded pieces
leads to machines that abstract to static analyses for context-free
reachability by simply bounding the stores. This technique allows us
to derive existing, more technically involved analyses, and a novel
pushdown analysis for delimited, composable control.

>>>>

Pushdown analysis improves upon finite-state analysis in precision and performance by not exploring spurious paths caused by improperly matched calls and returns.
%
Prior literature on pushdown higher-order flow analysis depends on complicated machinery that is difficult to understand, extend, and prove correct.
%
The machinery has no concrete counterpart --- there is little to no operational intuition as to why it works.
%
We show that these pushdown analyses have a similar core that can be explained with well-known techniques such as memoization and Abstracting Abstract Machines (AAM).
%
We use this interpretation to derive a novel pushdown analysis for delimited, composable control.
